%*************************************************
\documentclass[a4paper,10pt]{article}
\usepackage[brazil]{babel}
\usepackage[utf8]{inputenc}
%codigo
%\usepackage[latin1]{inputenc}
\usepackage{amsthm,amsfonts,amsmath,amssymb}
%img
\usepackage{graphicx}
\usepackage{subfig}
%tabela

%fim
%fim
\usepackage{listings}
\usepackage{makeidx}
\usepackage{enumerate}
\usepackage{hyperref}
\hypersetup{
  colorlinks,
  linkcolor=blue,
  filecolor=blue,
  urlcolor=blue,
  citecolor=blue
}

%titulo
\title{Curriculum Vitae}
\author{Leandro Kümmel Tria Mendes}
%inicio
\begin{document}
\begin{center} 
Curriculum Vitae
\end{center} 
\emph{Full name}: Leandro Kümmel Tria Mendes\\
\emph{Contato}: leandro.kummel@gmail.com | (55) (11) 97389-3876\\
\emph{Idade}: 27 anos (24/04/1986)\\
\emph{Nacionalidade}: Brasileiro\\
\section{Resumo}
Possui sólido conhecimento em desenvolvimento web, com mais de 9 anos de experiência em diversos projetos que vão desde, um simples \emph{Ensino a distância} a um complexo \emph{Leitor de notícias}.
\section{Objetivo}
Agregar valores e conhecimento. Projetos em prol da liberdade do conhecimento (software livre). 
Foco em estudos de data mining, aprendizado não-supervisionado e processamento de imagens. 
\section{Experiências}
\begin{itemize}
\item \emph{Coordenadoria de Projetos e Obras Unicamp (May/2013 - Nowaday) Trainee}: Responsible
for the management of SigPOd, that is an integrated system of project and buildings, and development of new modules (introduction of HTML5 for some of them).\textbf{[PHP, HTML5, JavaScript(frameworks JQuery, JQueryUI and PrototypeJS), Database: MySql, OS: Linux]}
\item \emph{Domane consultoria (Jan/2010 - Jan/2013) Freelance }: Several projects, all web. The most expressive, called SiGe (Integrated Business Management), this makes data collection company and presente reports, both, as table and chart (including ABC curve), and aid in decision made by leader. The layout development, of SiGe, has been written in HTML5 + JavaScript, especially in the implementation of the reports.\textbf{For web: [PHP5, JavaScript (frameworks: JQuery, JQueryUI and ExtJS), Database: PostgreSql and MySql, OS: Linux]; Others: [SheelScript and Python, OS: Linux]}
\item \emph{Instituto de Biologia Unicamp (Ago/2008 - Feb/2009) Scholarchip }: Web project \"Distance Education\", was responsible for develop, especially layouts of distance courses to public high school.\textbf{[PHP5, JavaScript (frameworks: JQuery and JQueryUI), Database: PostgreSql, Development OS: Linux, Production OS: MacOS]}
\item \emph{Griffon (Dez/2006 - Nov/2008) Formally employee }: From 2006/Dez to 2007/Jun had been hired to develop simple system, like Intranet and a web-communication between client and the service company, including a \"web-chat\".Nevertheless, from 2007/Jun until 2008/Nov, has been promoted to Director of Technology and started managing complex projects, such as, reading and clipping of news published at Federal Register (Journal Officiel), doing cluster and classification using unsupervised and supervised machine learning. Different computer languages were used: For web projects \textbf{[PHP5, HTML, JavaScript (AJAX)]} and for the reader/classifier \textbf{[Java and Python (scikit-learn , pyenhance and inflect - with brazilian dictionary)]}, \textbf{[Database: PostgreSql, OS: Linux]}
\item \emph{Mandic (Jan/2006 - Dez/2006) Freelance }:Coordinator and project developer WebMail 2.0. It was written in \textbf{[PHP5, AJAX and HTML], DataBase: PostgreSql, SO: Linux}.
\item \emph{Inova Unicamp (Junho/2004 - Dez/2005) Scholarchip }:Was developer and administrator websites of Agência de Inovação da Unicamp and business incubator Incamp.\textbf{[PHP4, HTML, Database: Mysql, OS: Linux]}
\end{itemize}
\end{document} 
